Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-20 paper/paper.tex
Use A instead of CComp, since we're using single letter names

Vismara and Valery \cite{DBLP:conf/mco/VismaraV08} implement the connectedness constraint by using a
branching rule which selects the next variable to be assigned. Let $\mathit{CComp}$ be the
set of variables already assigned to values different from $\bot$. The next variable to be assigned
is chosen within the set of unassigned variables which are the neighbour of at least one vertex of
$\mathit{CComp}$.  When this set is empty, all remaining unassigned variables are assigned to
$\bot$. We illustrate this in \cref{figure:restricted}.

@@

Finally, the two approaches for ensuring connectedness (branching and filtering) are complementary
and may be combined: at each step of the search, we select the next variable to be assigned within
the neighbors of $\mathit{CComp}$, and each time a vertex of $H$ is removed from a domain we filter
domains to ensure connectedness consistency.

>>>>

Vismara and Valery \cite{DBLP:conf/mco/VismaraV08} implement the connectedness constraint by using a
branching rule which selects the next variable to be assigned. Let $A$ be the
set of variables already assigned to values different from $\bot$. The next variable to be assigned
is chosen within the set of unassigned variables which are the neighbour of at least one vertex of
$A$.  When this set is empty, all remaining unassigned variables are assigned to
$\bot$. We illustrate this in \cref{figure:restricted}.

@@

Finally, the two approaches for ensuring connectedness (branching and filtering) are complementary
and may be combined: at each step of the search, we select the next variable to be assigned within
the neighbors of $A$, and each time a vertex of $H$ is removed from a domain we filter
domains to ensure connectedness consistency.
